surfing

### 2021-05-20 inst/surfing.Rmd
more work

\noindent where $p_H$ is a quantification of the beneficial home
ground effect.  Similar techniques have been used to account for the
first-move advantage in chess, and effective coordination between
members of doubles tennis teams.

@@

One suggestion is that Brazilians do worse on reef break and better on
point and beach break beaches.  We now assess the null that Brazilians
perform equally well on all types of beaches.

@@

```{r calcbrazodr,cache=TRUE}
braz <- c(0.0003,0.0005,0.0008, 0.001,0.002,0.005,0.01,0.02,0.03,0.05)
M <- do.call("rbind",lapply(braz,f))
M[,3] <- M[,3]-max(M[,3])
M
```

```{r}

plot(M[,2],M[,3]-max(M[,3]),type='b')
plot(M[,2],M[,3]-max(M[,3]),type='b',ylim=c(-0.3,0))
```

>>>>

\noindent where $p_H$ is a quantification of the beneficial home
ground effect.  Similar techniques have been used to account for the
first-move advantage in chess, and here we apply it to assess the
Brazilian  preference for reef-breaking waves.

@@

One suggestion is that Brazilians do worse on reef break and better on
point and beach break beaches.  We now assess the null that Brazilians
perform equally well on all types of beaches.  To that end, we create
a reified surfer, "Brazilian_beachtype", whose strength helps
Brazilian surfers when surfing on their (putative) preferred
beachtype.

@@

```{r calcbrazodr,cache=TRUE}
braz <- c(0.0003,0.0005,0.0008, 0.001,0.0015,0.002,0.003,0.004,0.005,0.007,0.01,0.015,0.02,0.03,0.05)
M <- do.call("rbind",lapply(braz,f))
M[,3] <- M[,3]-max(M[,3])
M
```

```{r}
plot(M[,2],M[,3]-max(M[,3]),type='b',xlab="Brazilian beachtype (log-odds)",ylab="support")
plot(M[,2],M[,3]-max(M[,3]),type='b',ylim=c(-0.3,0),xlab="Brazilian beachtype (log-odds)",ylab="support")
```
